### 2023-04-18 appendix.Rmd
removing covariances from the submission (only keep in discussion)

```{r Figure2, fig.width = 8, fig.height = 10, fig.cap = "Between-group discrepancies for all evaluation criteria split by *M*."}
### For the appendix -- other splits for the main results as plot (N is most important)
# Plot the results, by M
ldf %>% 
  group_by(method, Objective, M) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>% 
  ggplot(aes(x = M, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 2:5)
```

```{r Figure3, fig.width = 8, fig.height = 10, fig.cap = "Between-group discrepancies for all evaluation criteria split by *SD*."}
# Plot the results, by SD
ldf %>% 
  group_by(method, Objective, SD) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>% 
  ggplot(aes(x = SD, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 1:3)
```

```{r Figure4, fig.width = 8, fig.height = 10, fig.cap = "Between-group discrepancies for all evaluation criteria split by *K*."}
# Plot the results, by K
ldf %>% 
  group_by(method, Objective, K) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>% 
  ggplot(aes(x = K, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 2:4)
```

```{r Figure5, fig.width = 8, fig.height = 10, fig.cap = "Between-group discrepancies for all evaluation criteria split by *r*."}
# Plot the results, by r
ldf %>% 
  group_by(method, Objective, r) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>% 
  ggplot(aes(x = r, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 0:5 / 10)
```

>>>>

```{r Figure2, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness and kurtosis (split by the number of features, averaged across the remaining variables that varied in the simulation)."}
### For the appendix -- other splits for the main results as plot (N is most important)
# Plot the results, by M (number of features)
ldf %>% 
  group_by(method, Objective, M) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis"),
        ")]"
      )
    ) 
  ) %>% 
  ggplot(aes(x = M, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy") +
  xlab("Number of features") +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 2:5)
```

```{r Figure3, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness and kurtosis (split by *SD*, averaged across the remaining variables that varied in the simulation)."}
# Plot the results, by SD
ldf %>% 
  group_by(method, Objective, SD) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis"),
        ")]"
      )
    ) 
  ) %>% 
  ggplot(aes(x = SD, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy")+
  xlab(expression(italic(SD))) +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 1:3)
```

```{r Figure4, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness and kurtosis (split by *K*, averaged across the remaining variables that varied in the simulation)."}
# Plot the results, by K
ldf %>% 
  group_by(method, Objective, K) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis"),
        ")]"
      )
    ) 
  ) %>% 
  ggplot(aes(x = K, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy")+
  xlab(expression(italic(K))) +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 2:4)
```

```{r Figure5, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness and kurtosis (split by *r*, averaged across the remaining variables that varied in the simulation)."}
# Plot the results, by r
ldf %>% 
  group_by(method, Objective, r) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis"),
        ")]"
      )
    ) 
  ) %>% 
  ggplot(aes(x = r, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy")+
  xlab(expression(italic(r))) +
  theme_bw(base_size = 16) + 
  scale_x_continuous(breaks = 0:5 / 10)
```

### 2023-04-18 paper.Rmd
removing covariances from the submission (only keep in discussion)

    Anticlustering refers to the process of partitioning elements into disjoint groups with the goal of obtaining high between-group similarity and high within-group heterogeneity. Anticlustering thereby reverses the logic of its better known twin---cluster analysis---and is usually approached by maximizing instead of minimizing a clustering objective function. Introducing k-plus, this paper presents an extension of the classical k-means objective to maximize between-group similarity in anticlustering applications. The k-plus criterion represents between-group similarity as discrepancy in distribution moments (means, variance, higher order moments, and covariances), whereas the k-means criterion only reflects the degree to which groups differ in their means. While constituting a new criterion for anticlustering, it is surprisingly shown that k-plus anticlustering can be implemented by optimizing the original k-means criterion after the input data has been augmented with additional variables. A computer simulation and practical examples show that k-plus anticlustering achieves high between-group similarity with regard to multiple objectives. In particular, optimizing between-group similarity with regard to variances usually does not compromise similarity with regard to means; the k-plus extension is therefore generally preferred over classical k-means anticlustering. Examples are given on how k-plus anticlustering can be applied to real norming data using the open source R package `anticlust`, which is freely available via CRAN (https://cran.r-project.org/package=anticlust).

@@

keywords          : "Anticlustering, k-means, k-plus, variance, covariance, skewness, kurtosis, stimulus selection"
wordcount         : "4992"

@@

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that quantifies between-group similarity as discrepancy with regard to several distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance, covariances, and higher order moments such as skewness and kurtosis. After formally introducing the k-plus objective, a simulation study shows that k-plus anticlustering is well-suited to create groups having minimal differences according to multiple distribution characteristics. Practical examples illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust` [@papenberg2020; @R-anticlust], an extension to the popular statistical programming language R [@R-base].

@@

## Covariances

Because the covariance is also defined as an expected value, the k-plus logic can be extended to minimize differences with regard to covariance structure. The covariance between two variables $x = (x_1, \ldots, x_N)$ and $y = (y_1, \ldots, y_N)$ is defined as

$$
\frac{1}{N} \sum\limits_{i=1}^{N} (x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}}).
$$

Thus, to maximize between-group similarity with regard to covariance structure, it is possible to augment the data set with an additional variable for each pair of variables $x$ and $y$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$.

@@

To thoroughly evaluate the k-plus approach to anticlustering, three specific k-plus criteria were implemented in a simulation study: (i) "standard" k-plus anticlustering, minimizing differences with regard to group means and variances; (ii) k-plus *skew/kurtosis*, minimizing differences with regard to group means, variances, skewness and kurtosis; (iii) k-plus *correlation*, minimizing differences with regard to group means, variances and covariance structure. To implement all k-plus objectives, the unweighted sum approach was employed. Thus, to optimize a k-plus criterion, the original data set was augmented to incorporate the additional criteria and all variables---the original and the augmented variables---were $z$-standardized. Subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set. The three k-plus methods were compared to (i) k-means anticlustering, minimizing differences with regard to group means, (ii) diversity anticlustering, maximizing the sum of pairwise Euclidean distances within groups, (iii) a random allocation of elements to groups.

@@

# Make long format
ldf <- pivot_longer(
  df,
  cols = paste0(c("means", "sd", "skew", "kur", "cor"), "_obj"),
  names_to = "Objective",
  names_pattern = "(.*)_obj"
)

## Global results, aggregated across all simulation variables
tab <- ldf %>% 
  group_by(method, Objective) %>% 
  summarise(Mean = round(mean(value), 3)) %>% 
  pivot_wider(names_from = Objective, values_from = Mean) %>% 
  select(c(means, sd, skew, kur, cor))

colnames(tab) <- c("",
  "$\\Delta M$", 
  "$\\Delta \\mathit{SD}$",
  "$\\Delta \\mathit{Skew}$",
  "$\\Delta \\mathit{Kurtosis}$",
  "$\\Delta \\mathit{Cor}$"
)

apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average global between-group discrepancy with regard to means, standard deviations, skewness, kurtosis, and correlations. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$ or $K = 4$).",
  escape = FALSE,
  align = c("r")
)

@@

```{r Figure1, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness, kurtosis and correlations (split by $N$, averaged across the remaining variables that varied in the simulation)."}

@@

ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis", "Cor"),
        ")]"
      )
    ) 
  ) %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy")+
  xlab(expression(italic(N))) +
  theme_bw(base_size = 16) + 
  scale_x_continuous(
    breaks = axis_ticks, 
    labels = axis_labels
  )

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that k-plus anticlustering is capable of addressing multiple objectives at the same time---especially when $N$ increases. However, while k-plus anticlustering was capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria made it more difficult to fulfill each single criterion: k-plus skew/kurtosis and k-plus correlation performed worse at minimizing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$ than standard k-plus. However, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

@@

Generally, it should be noted that diversity anticlustering is a good all-rounder method that tends to address all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. As a side note, apart from k-plus correlation, diversity anticlustering was the only method that equalized correlation structure among groups. To the best of my knowledge, this observation has not been made previously, even though the maximum diversity problem has been widely studied.

The Appendix includes additional figures splitting the simulation results according to the other variables that varied between simulation runs (number of features; correlation between features; standard deviation of features; number of groups). Here, the only meaningful moderating effect on anticlustering performance was that k-plus correlation was more strongly impaired than other methods when the number of features increased. Because the number of covariances increases quadratically when the number of features increases, it gets comparatively more difficult to fulfill the correlation objective with a higher number of features.

@@

kplus_anticlustering(
  features,
  K = 9,
  variance = TRUE,
  skew = TRUE,
  kurtosis = FALSE,
  covariances = FALSE,
  moments = NULL,
  method = "local-maximum",
  standardize = TRUE
)
```

The function call takes about 10 seconds on a contemporary personal computer. The function `kplus_anticlustering()` has four boolean arguments to specify whether variance, skewness, kurtosis and covariances should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default---corresponding to the understanding that k-plus is an extension to k-means that at least equalizes variances in addition to means. The arguments corresponding to skewness, kurtosis and covariance have to be specifically "turned on", i.e., by setting them to `TRUE` in the function call of `kplus_anticlustering()`. If other higher order moments should be included as part of the optimization, the optional argument `moments` can be used to specify the desired moments as an integer vector. The argument `method = "local-maximum"` ensures that the k-plus criterion is optimized using the local maximum search method described in the previous section. The argument `K` describes the number of groups. By default, the function ensures that all features are standardized before the optimization starts; in particular, this option enforces that all k-plus criteria receive the same weight during the optimization process. This behaviour can be adjusted using the boolean argument `standardize`.

@@

[^standardkplus]: I refer to *standard* k-plus anticlustering as the minimization of differences in means and variances, but not in higher order moments or covariances.

@@

Anticlustering is a partitioning method that aims for high between-group similarity and high within-group heterogeneity. In this paper, I presented the k-plus criterion for anticlustering, which focuses on maximizing between-group similarity. K-plus represents between-group similarity as discrepancies in distribution moments between groups: means, variances, skewness, kurtosis, higher order moments, and covariances. Depending on the application, a different subset of these objectives can be included in the anticlustering process. The k-plus criterion is an extension of the classical k-means criterion, which only reflects how similar groups are with regard to their means. Interestingly, however, the k-plus extension does not change the original k-means criterion because additional criteria can be incorporated by augmenting the input data.

@@

>>>>

    Anticlustering refers to the process of partitioning elements into disjoint groups with the goal of obtaining high between-group similarity and high within-group heterogeneity. Anticlustering thereby reverses the logic of its better known twin---cluster analysis---and is usually approached by maximizing instead of minimizing a clustering objective function. Introducing k-plus, this paper presents an extension of the classical k-means objective to maximize between-group similarity in anticlustering applications. The k-plus criterion represents between-group similarity as discrepancy in distribution moments (means, variance, skewness, and higher order moments), whereas the k-means criterion only reflects the degree to which groups differ in their means. While constituting a new criterion for anticlustering, it is surprisingly shown that k-plus anticlustering can be implemented by optimizing the original k-means criterion after the input data has been augmented with additional variables. A computer simulation and practical examples show that k-plus anticlustering achieves high between-group similarity with regard to multiple objectives. In particular, optimizing between-group similarity with regard to variances usually does not compromise similarity with regard to means; the k-plus extension is therefore generally preferred over classical k-means anticlustering. Examples are given on how k-plus anticlustering can be applied to real norming data using the open source R package `anticlust`, which is freely available via CRAN (https://cran.r-project.org/package=anticlust).

@@

keywords          : "Anticlustering, k-means, k-plus, variance, skewness, kurtosis, stimulus selection"
wordcount         : "4992"

@@

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that quantifies between-group similarity as discrepancy with regard to several distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance and higher order moments such as skewness and kurtosis. After formally introducing the k-plus objective, a simulation study shows that k-plus anticlustering is well-suited to create groups having minimal differences according to multiple distribution characteristics. Practical examples illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust` [@papenberg2020; @R-anticlust], an extension to the popular statistical programming language R [@R-base].

@@

@@

To thoroughly evaluate the k-plus approach to anticlustering, two k-plus criteria were implemented in a simulation study: (i) "standard" k-plus anticlustering, minimizing differences with regard to group means and variances; (ii) k-plus *skew/kurtosis*, minimizing differences with regard to group means, variances, skewness and kurtosise. To implement the k-plus objectives, the unweighted sum approach was employed. Thus, to optimize a k-plus criterion, the original data set was augmented to incorporate the additional criteria and all variables---the original and the augmented variables---were $z$-standardized. Subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set. The three k-plus methods were compared to (i) k-means anticlustering, minimizing differences with regard to group means, (ii) diversity anticlustering, maximizing the sum of pairwise Euclidean distances within groups, (iii) a random allocation of elements to groups.

@@

# Make long format
ldf <- pivot_longer(
  df,
  cols = paste0(c("means", "sd", "skew", "kur"), "_obj"),
  names_to = "Objective",
  names_pattern = "(.*)_obj"
)

ldf <- ldf[ldf$method != "k-plus-correlation", ] # removed because this deserves closer attention than what was given in the paper; check out the first version of the preprint for the previous results

## Global results, aggregated across all simulation variables
tab <- ldf %>% 
  group_by(method, Objective) %>% 
  summarise(Mean = round(mean(value), 3)) %>% 
  pivot_wider(names_from = Objective, values_from = Mean) %>% 
  select(c(means, sd, skew, kur))

colnames(tab) <- c("",
  "$\\Delta M$", 
  "$\\Delta \\mathit{SD}$",
  "$\\Delta \\mathit{Skew}$",
  "$\\Delta \\mathit{Kurtosis}$"
)

apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average global between-group discrepancy with regard to means, standard deviations, skewness and kurtosis. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$ or $K = 4$).",
  escape = FALSE,
  align = c("r")
)

@@

```{r Figure1, fig.width = 8, fig.height = 10, fig.cap = "Results of the simulation study: Depicts the performance of the anticlustering methods with regard to minimizing discrepancy in means, variances, skewness and kurtosis (split by $N$, averaged across the remaining variables that varied in the simulation)."}

@@

ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur"),
      labels = paste0(
        "Delta[italic(",
        c("M", "SD", "Skew", "Kurtosis"),
        ")]"
      )
    ) 
  ) %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free", labeller = label_parsed) + 
  ylab("Mean discrepancy")+
  xlab(expression(italic(N))) +
  theme_bw(base_size = 16) + 
  scale_x_continuous(
    breaks = axis_ticks, 
    labels = axis_labels
  )

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that k-plus anticlustering is capable of addressing multiple objectives at the same time---especially when $N$ increases. However, while k-plus anticlustering was capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria made it more difficult to fulfill each single criterion: k-plus skew/kurtosis performed worse at minimizing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$ than standard k-plus that only considered the mean and variances. However, as intended, k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$ and at the same time, this k-plus objective maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

@@

Generally, it should be noted that diversity anticlustering is a good all-rounder method that tends to address all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. The Appendix includes additional figures splitting the simulation results according to the other variables that varied between simulation runs (number of features; correlation between features; standard deviation of features; number of groups).

@@

kplus_anticlustering(
  features,
  K = 9,
  variance = TRUE,
  skew = TRUE,
  kurtosis = FALSE,
  moments = NULL,
  method = "local-maximum",
  standardize = TRUE
)
```

The function call takes about 10 seconds on a contemporary personal computer. The function `kplus_anticlustering()` has three boolean arguments to specify whether variance, skewness and kurtosis should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default---corresponding to the understanding that k-plus is an extension to k-means that at least equalizes variances in addition to means. The arguments corresponding to skewness and kurtosis have to be specifically "turned on", i.e., by setting them to `TRUE` in the function call of `kplus_anticlustering()`. If other higher order moments should be included as part of the optimization, the optional argument `moments` can be used to specify the desired moments as an integer vector. The argument `method = "local-maximum"` ensures that the k-plus criterion is optimized using the local maximum search method described in the previous section. The argument `K` describes the number of groups. By default, the function ensures that all features are standardized before the optimization starts; in particular, this option enforces that all k-plus criteria receive the same weight during the optimization process. This behaviour can be adjusted using the boolean argument `standardize`.

@@

[^standardkplus]: I refer to *standard* k-plus anticlustering as the minimization of differences in means and variances, but not in higher order moments.

@@

Anticlustering is a partitioning method that aims for high between-group similarity and high within-group heterogeneity. In this paper, I presented the k-plus criterion for anticlustering, which focuses on maximizing between-group similarity. K-plus represents between-group similarity as discrepancies in distribution moments between groups: means, variances, skewness, kurtosis, and higher order moments. Depending on the application, a different subset of these objectives can be included in the anticlustering process. The k-plus criterion is an extension of the classical k-means criterion, which only reflects how similar groups are with regard to their means. Interestingly, however, the k-plus extension does not change the original k-means criterion because additional criteria can be incorporated by augmenting the input data.

@@

It should be noted that because the covariance is defined as an expected value, the k-plus logic can be extended to minimize differences with regard to covariance, a possibility that was not investigated in the current paper. The covariance between two variables $x = (x_1, \ldots, x_N)$ and $y = (y_1, \ldots, y_N)$ is defined as $\frac{1}{N} \sum\limits_{i=1}^{N} (x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. Thus, to maximize between-group similarity with regard to covariance structure, it is possible to augment the data set with an additional variable for each pair of variables $x$ and $y$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. Future research should examine how the k-plus approach can be adapted to including covariances, including a discussion of how to select weights for the possibly high number of additional variables. The unweighted standardization approach presented here may serve as a starting point for investigation.
